---
title: "p8105_hw1_CongyangXie"
author: "Congyang"
date: "9/25/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1

* Create a data frame comprised of:
  + random sample of size 10 from a standard Normal distribution
  + logical vector indicating whether elements of the sample are greater than 0
  + a character vector of length 10
  + factor vector of length 10, with 3 different factor “levels”

```{r}

library(ggplot2)
library(schoolmath)

set.seed(1)
c1 = rnorm(10)
c2 = is.positive(c1)
c3 = rep_len('ImAChar', 10)
c4 = factor(sample(c("Lv1","Lv2","Lv3"), 10, replace = TRUE), ordered = TRUE, levels  = c("Lv1","Lv2","Lv3"))

df1 <- data.frame(c1, c2, c3, c4)

```
Try to take the mean of each variable in your dataframe. What works and what doesn’t?
```{r}
library(tidyverse)

mean(pull(df1, 1))
mean(pull(df1, 2))
mean(pull(df1, 3))
mean(pull(df1, 4))

```

The first mean is simply the arithmetic average. The true is 1, false is 0. But the third and last ones are not numeric or logical data, so their mean cannot be calculated.

```{r, results='hide'}

mean(as.numeric(pull(df1,2)))
mean(as.numeric(pull(df1,3)))
mean(as.numeric(pull(df1,4)))

```
 When using as.numeric(), it turns characters in column 3 to NAs and 3 ordinal factors in column 4 to 1, 2, 3.
  
# Problem 2

* Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code, including:
  
  + the data in this dataset, including names / values of important variables
  + the size of the dataset (using nrow and ncol)
  + the mean flipper length

```{r}

data("penguins", package = "palmerpenguins")

```
  + The variables in the penguins are: `r names(penguins)`. 
  + The peguines dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
  + "species" is a factor variable, which has unique values: `r levels(pull(penguins, species))`.
  + "island" is a factor variable, which has unique values: `r levels(pull(penguins, island))`.
  + "sex" is a factor variable, which has unique values: `r levels(pull(penguins, sex))`.
  + "bill_length_mm" is a numeric variable, whose mean is `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)`, median is `r median(pull(penguins, bill_length_mm), na.rm = TRUE)`, standard deviation is `r sd(pull(penguins, bill_length_mm), na.rm = TRUE)`, range is `r max(pull(penguins, bill_length_mm), na.rm = TRUE) - min(pull(penguins, bill_length_mm), na.rm = TRUE)`.
  + "bill_depth_mm" is a numeric variable, whose mean is `r mean(pull(penguins, bill_depth_mm), na.rm = TRUE)`, median is `r median(pull(penguins, bill_depth_mm), na.rm = TRUE)`, standard deviation is `r sd(pull(penguins, bill_depth_mm), na.rm = TRUE)`, and range is `r max(pull(penguins, bill_depth_mm), na.rm = TRUE) - min(pull(penguins, bill_depth_mm), na.rm = TRUE)`.
  + "flipper_length_mm" is a numeric variable, whose mean is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`, median is `r median(pull(penguins, flipper_length_mm), na.rm = TRUE)`, standard deviation is `r sd(pull(penguins, flipper_length_mm), na.rm = TRUE)`, and range is `r max(pull(penguins, flipper_length_mm), na.rm = TRUE) - min(pull(penguins, flipper_length_mm), na.rm = TRUE)`.
  + "body_mass_g" is a numeric variable, whose mean is `r mean(pull(penguins, body_mass_g), na.rm = TRUE)`, median is `r median(pull(penguins, body_mass_g), na.rm = TRUE)`, standard deviation is `r sd(pull(penguins, body_mass_g), na.rm = TRUE)`, and range is `r max(pull(penguins, body_mass_g), na.rm = TRUE) - min(pull(penguins, body_mass_g), na.rm = TRUE)`.
  + "year" has unique values: `r unique(pull(penguins, year), na.rm = TRUE)`.



